```{r}
library(rfisheries)
library(reshape2)
library(ggplot2)
```

```{r}
species <- species_codes(progress = "none")
tunas <- grep("Tuna", species$english_name)
```

```{r}
who <- c("TUX", "COD", "VET", "NPA")
by_species <- lapply(who, function(x) landings(species=x))
names(by_species) <- who
```

```{r}
dat <- melt(by_species, id = c('catch', 'year'))
names(dat) = c("catch", "year", "a3_code")
```

Tidy data is easy to plot:

```{r}
ggplot(dat, aes(year, catch)) + geom_line() + facet_wrap(~a3_code, scales="free_y")
```




```{r}
library(data.table)
species <- data.table(species)
setkey(species, "a3_code")
code_names <- species[who, scientific_name]
```

```{r}
code_names[[2]] <- factor(code_names[[2]])
```


or as a named string,

```{r}
codes <- code_names$scientific_name
names(codes) <- code_names$a3_code
codes
```


We set column classes appropriately:

```{r}
dat$year = as.Date(as.character(dat$year), format="%Y")
dat$a3_code = as.factor(dat$a3_code)
```

```{r}
library(reml)
```

We add essential metadata to the table definiting the column headings and their units: 

```{r}
dat <- data.set(dat, 
                col.defs = c(catch = "Global Landings of fish",
                             year = "the year for which data was reported",
                             a3_code = "a 3 digit country code"),
                unit.defs = list(catch = c("tonnes", precision = 1),
                                 year = "YYYY",
                                 a2_code = codes))
                  
```

If names are not provided for `col.defs` and `unit.defs` reml will assume these are given in the order of the columns of the data frame. 


```{r warnings=FALSE}
description = "Landings data for several species by year, from the OpenFisheries database"
eml_write(dat = dat, 
          title = "Landings Data", 
          description = description, 
          creator = "Karthik Ram <karthik@ropensci.org>", 
          file = "landings.xml")
```


## Publish to rfigshare

```{r}
eml_publish("landings.xml", 
            description=description, 
            categories="Ecology", 
            tags="fisheries", 
            destination = "figshare",
            visibility="public")
```


## Adding Location context with GBIF

```{r, eval=FALSE}
library(rgbif)
omany <- failwith(NULL, occurrencelist_many)
locations <- llply(as.list(code_names$scientific_name), omany, .progress = "none")
names(locations) = who
species_loc <- lapply(locations, function(x) data.frame(species = x[1], Lat = x[3], Long = x[4]))
loc <- melt(species_loc, id = names(species_loc[[1]]))
names(loc) = c("scientific_name", "Lat", "Long", "a3_code")
a = join(dat, loc, by="a3_code")

```





Richer GBIF record ...

```{r, eval=FALSE}
omany <- failwith(NULL, occurrencelist)
locations <- llply(as.list(code_names$scientific_name), omany, format="darwin", .progress = "none")
gbif_dat <- lapply(locations, gbifdata, minimal = FALSE)
```



